Development of a educational and sustainable robotic platform for children and adults

### 2014-03-04 doc/paper.tex
autocommited by makefile

%\usepackage[sortcites=true, style=authoryear,natbib=true]{biblatex}
\usepackage{biblatex}
\bibliography{bibliography}

@@

\section{Introduction}
Getting children in touch with technology is important in todays technologically advanced society. In schools technology (specifically electrical engineering and programming) is often taught using robots. Robots are well suited for children since they allow interaction with the reality in contrast to arbitrary technology related exercises such as programming exercises which doesn't affect the real world.\newline 
Since schools are required to save money, robots used for teaching stay property of the schools. Therefore children usually cannot take the robot home to work with it. In addition modification of robot is usually not permitted which reduces potential learning experiences. Giving students the full control over all possibilities of the robot requires them to own the robot. This requires to robot to be cheap, extendable and suitable for educational purposes.\newline
The development of a robot platform for educational purpose requires requirement engineering, market research and evaluation of robots which are already used in education. Once the research is completed a new robot platform can be constructed taking the research results into account. The goal is to develop such an educational robot platform with regard to the target user group, their needs and educational concepts.
\section{Requirement Analysis / Project Goals}
User group of a robot can be categorized into different groups regardless of their age:
\begin{description}
\item[Beginner] \hfill \\ Beginners have little to no experience with robots. They need extensive assistance to perform tasks such as soldering and programming. For programming graphical programming languages (such as minibloq or ModKit) or languages providing a high level of abstraction (such as Wiring), 
\item[Advanced] \hfill \\ Advanced users have advanced experience with robots and robotics. Most programming and soldering tasks are done independently; working knowledge is utilized to solve new and unknown tasks.  
\item[Expert] \hfill \\ Expert users understand all aspects of robots and their internals. New challenges are faced with ease.
\end{description}

>>>>

%\usepackage[sortcites=true, style=authoryear,natbib=true]{biblatex}
\usepackage{biblatex}
\bibliography{bibliography}
\nocite{*}

@@

\section{Introduction}
Getting children in touch with technology is important in todays technologically advanced society. In schools technology (specifically electrical engineering and programming) is often taught using robots. Robots are well suited for children since they allow interaction with the reality in contrast to arbitrary technology related exercises such as programming exercises which doesn't affect the real world.\newline 
Since schools are required to save money, robots used for teaching stay property of the schools. Therefore children usually cannot take the robot home to work with it. In addition modification of robot is usually not permitted which reduces potential learning experiences. Giving students the full control over all possibilities of the robot requires them to own the robot. This requires to robot to be cheap, extensible and suitable for educational purposes.\newline
The development of a robot platform for educational purpose requires requirement engineering, market research and evaluation of robots which are already used in education. Once the research is completed a new robot platform can be constructed taking the research results into account. The goal is to develop such an educational robot platform with regard to the target user group, their needs and educational concepts.
\section{Requirement Analysis / Project Goals}
User group of a robot can be categorized into different groups regardless of their age:
\begin{description}
\item[Beginner] \hfill \\ Beginners have little to no experience with robots. They need extensive assistance to perform tasks such as soldering and programming. For programming graphical programming languages (such as minibloq or ModKit) or languages providing a high level of abstraction (such as Wiring), 
\item[Advanced] \hfill \\ Advanced users have advanced experience with robots and robotics. Most programming and soldering tasks are done independently; working knowledge is utilized to solve new and unknown tasks.  
\item[Expert] \hfill \\ Expert users understand all aspects of robots and their internals. New challenges are faced with ease.
\end{description}
